\documentclass[10pt]{article}
\usepackage[margin=3cm]{geometry}

\usepackage{array, xcolor}
\definecolor{lightgray}{gray}{0.8}
\newcolumntype{L}{>{\raggedleft}p{0.14\textwidth}}
\newcolumntype{R}{p{0.8\textwidth}}
\newcommand\VRule{\color{lightgray}\vrule width 0.5pt}

\title{\bfseries\Huge Sam A. Markelon}
\author{
  markelon@protonmail.com\\
  smarky7cd.github.io
}
\date{}

\begin{document}
\maketitle

\section*{Education}
\begin{tabular}{L!{\VRule}R}
  2020--\quad&{\bf PhD in Computer Science, University of Florida}\\
  		     &\quad Florida Institute for Cybersecurity Research\\[5pt]
  2016--2020&{\bf BS in Computer Science, University of Connecticut}\\
            &\quad Minor in Mathematics \\
            &\quad Summa Cum Laude\\
            &\quad Honors Scholar
\end{tabular}

\section*{Professional Experience}
\begin{tabular}{L!{\VRule}R}
  Summer 2019&{\bf NCC Group (New York, NY)}\\
             &\quad Cryptography Services Intern\\[5pt]
  Summer 2018&{\bf Institut de Physique Nucléaire d'Orsay (Orsay, France)}\\
             &\quad Scientific Computing Intern\\[5pt]
  Summer 2017&{\bf Jefferson National Laboratory (Newport News, VA)}\\
             &\quad Software Engineering Intern
\end{tabular}

\section*{Teaching Experience}

All as undergraduate teaching assistant at the University of Connecticut.\\[5pt]

\begin{tabular}{L!{\VRule}R}
  Spring 2020 Fall 2019 &{\bf CSE 3400: Introduction to Computer and Network Security}\\[10pt]
  Spring 2019&{\bf CSE 3150: C++ Essentials}\\[5pt]
  Fall 2018&{\bf CSE 2050: Data Structures and Object Oriented Programming}\\
\end{tabular}

\section*{Awards and Grants}
\begin{tabular}{L!{\VRule}R}
  2020&{\bf University of Florida Graduate School Preeminence Award}\\[5pt]
  2019&{\bf Barry M. Goldwater Scholarship}\\[5pt]
  2018&{\bf University of Connecticut IDEA Grant}\\
      &\quad NTRUEncrypt implementation and usage research.\\[5pt]
  2016&{\bf University of Connecticut STEM Scholar}
\end{tabular}

\section*{Publications}
\begin{enumerate}
  
\subsection*{Journal and Conference Papers}

\item {\bf The DecCert PKI: A Solution to Decentralized Identity Attestation and Zooko's Triangle}\\
Sam A. Markelon and John True.\\
IEEE DAPPs 2022.

\item {\bf A Semi-Quantum Extended B92 Protocol and its Analysis}\\
Walter O. Krawec and Sam A. Markelon. \\
Proc. SPIE 11391, Quantum Information Science, Sensing, and Computation XII, (24 April 2020).


\item {\bf Genetic Algorithm to Study Practical Quantum Adversaries}\\
  W.O. Krawec and S.A. Markelon.\\
  ACM GECCO (2018) Kyoto Japan, pages 1270-1277.

\subsection*{Posters and Poster Papers}

\item {\bf Discovery of Robust Protocols for Secure Quantum Cryptography}\\
  W.O Krawec and S.A. Markelon.\\
  ACM GECCO (2019) New York, NY, pages 379-380.

\item {\bf gemcWeb: A Cloud Based Nuclear Physics Simulation Software}\\
  Sam A. Markelon.\\
  APS DNP CEU Poster Session, Fall 2017.

\subsection*{Preprints}

\item {\bf Covert Message Passing over Public Internet Platforms Using Model-Based Format-Transforming Encryption}\\
  Luke A. Bauer, James K. Howes IV, Sam A. Markelon, Vincent Bindschaedler, and Thomas Shrimpton.\\
  arXiv:2110.07009.

\end{enumerate}

\section*{Extracurricular Activities}
\begin{itemize}

\item {\bf Association of Computing Machinery Student Chapter}\\
\quad Information Security (Cryptography) Group Leader

\item {\bf Upsilon Pi Epsilon}

\item {\bf UConn Mixed Martial Arts Club}\\
\quad Vice President, Treasurer

\end{itemize}

\end{document}
